Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-19 paper/paper.tex
arreglando fórmulas
Update

To evaluate each subtask, we count correct, partial, missing, and spurious
annotations, and weight them according to an $F_1$ measure, independently per task.

>>>>

To evaluate each subtask, we count correct, incorrect, partial, missing, and spurious
annotations, and weight them according to an $F_1$ measure, independently per task.
Partial annotations~(i.e., where predicted entities overlap with the gold standard) are counted as half the value of correct annotations.
